Using tours to visually investigate properties of new projection pursuit indexes with application to problems in physics

### 2019-01-10 scagnostics.Rmd
spring erfiles

bibliography: bibliography.bib
output: rticles::asa_article
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{amssymb}
  - \usepackage{xcolor}
---

>>>>

bibliography: bibliography.bib
output: rticles::springer_article
header-includes:
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{amssymb}
  - \usepackage{xcolor}
---
